Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2022-05-13 reports/manuscript.Rmd
Move references to supp file

documentclass     : "apa6"
classoption       : "man"
csl               : vancouver-brackets-meta.csl
output            : papaja::apa6_pdf
header-includes:
    - \usepackage{makecell}
    - \usepackage{booktabs}
    - \usepackage{colortbl}
params:
    nocite_list: !r list()
nocite            : "`r params$nocite_list`"
---

@@

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
References marked with an asterisk indicate studies which were included in the synthesis.
<div id = "refs"></div>
\endgroup

>>>>

documentclass     : "apa6"
classoption       : "man"
csl               : nature.csl
output            : papaja::apa6_pdf
header-includes:
    - \usepackage{makecell}
    - \usepackage{booktabs}
    - \usepackage{colortbl}
---

@@

<div id = "refs"></div>
